Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
paper changes
trying to get changes

Because this task is embarassingly parallel and nearly 100% of the computation code can be parallelized (disregarding any uneven divisions of the space by the number of processors), we achieve the Amdahl's Law optimal speedup bound of (with $B$ of 0):

@@

Varying Iterations:

Varying Quality Factor:
We define the quality factor in this case for how many times smaller the Euler method used for $g_{\textnormal{fine}}$ is compared to the Euler method used for $g_{\Delta t}$

Changing the ODE

TODO ashi sort out the figure and match and replace if needbe

@@

@@

Note that each processor receives information from only those adjacent to it; that is, the top left processor in the graphic does not communicate directly with the bottom right processor in the graphic. Rather, information is passed only along shared boundary points to propagate the wave equation. We run this code for two different grid sizes, $128\times 128$ and $256\times 256$, as well as in serial.

@@

\begin{center}
\begin{tabular}{|c|c|} \hline
($N_x, N_y$) & Time (seconds)\\ \hline
(128, 128) & 0.987\\ \hline
(256, 256) & 7.889\\ \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) \\ \hline
(128, 128) & 2 & 2 &  \\ \hline
(128, 128) & 4 & 2 & 2.31 \\ \hline
(128, 128) & 4 & 4 &  \\ \hline
(128, 128) & 8 & 8 &  \\ \hline
(256, 256) & 2 & 2 & 2.57 \\ \hline
(256, 256) & 4 & 2 & 11.32 \\ \hline
(256, 256) & 4 & 4 & 13.65 \\ \hline
(256, 256) & 8 & 8 & 17.44 \\ \hline
\end{tabular}
\end{center}

>>>>

Because this task is embarassingly parallel and nearly 100\% of the computation code can be parallelized (disregarding any uneven divisions of the space by the number of processors), we achieve the Amdahl's Law optimal speedup bound of (with $B$ of 0):

@@

%Varying Iterations:

Varying Quality Factor:
We define the quality factor in this case for how many times smaller the Euler
method used for $g_{\textnormal{fine}}$ is compared to the Euler method used for
$g_{\Delta t}$.

@@

Figure~\ref{fig:run_v_cpu} shows the running time (wall clock) for the Parareal
algorithm

@@

Note that each processor receives information from only those adjacent to it; that is, the top left processor in the graphic does not communicate directly with the bottom right processor in the graphic. Rather, information is passed only along shared boundary points to propagate the wave equation. We run this code for three different grid sizes: $128\times 128$, $256\times 256$, and $512\times 512$, in both serial and parallel.

@@

\begin{center}
\begin{tabular}{|c|c|} \hline
($N_x, N_y$) & Time (seconds)\\ \hline
(128, 128) & 0.987\\ \hline
(256, 256) & 7.889\\ \hline
(512, 512) & 63.913\\ \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) \\ \hline
(128, 128) & 2 & 2 &  \\ \hline
(128, 128) & 4 & 2 & 2.31 \\ \hline
(128, 128) & 4 & 4 &  \\ \hline
(128, 128) & 8 & 8 &  \\ \hline
(256, 256) & 2 & 2 & 2.57 \\ \hline
(256, 256) & 4 & 2 & 11.32 \\ \hline
(256, 256) & 4 & 4 & 13.65 \\ \hline
(256, 256) & 8 & 8 & 17.44 \\ \hline
(512, 512) & 2 & 2 & \\ \hline
(512, 512) & 4 & 2 &  \\ \hline
(512, 512) & 4 & 4 &  \\ \hline
(512, 512) & 8 & 8 &  \\ \hline
\end{tabular}
\end{center}
